\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-11 smurf_paper.tex
a few more minor edits

In order to reduce the impact of low-frequency noise on the final
maps, \scuba\ scan strategies have been designed to provide: (i) good
cross-linking (visiting every point of the mapped area on several
different time scales, and at different scan angles); and (ii) minimal
accelerations to reduce turn-around overheads (which could be quite
large given the 600\,arcsec\,s$^{-1}$ maximum scan speed). For areas
larger than the array footprint a closed ``PONG'' pattern is used, in
which the boresight travels in approximately straight lines and
``bounces'' off the edges at 45\,degree angles until the area is
uniformly filled in. It is also usually combined with a rotation
through a number of fixed position angles to create a ``rotating
PONG'' with even better cross-linking. For smaller areas (of order the
array footprint, or pont sources), in which the PONG turn-around
overheads would be large, a ``constant velocity daisy'' (CV Daisy) is
used.  Here the telescope moves in a circle, whose centre also slowly
traces out a small circle. For a more complete description of the
\scuba\ observing modes, see Section~5 in \citet{holland2012} and also
\citet{2010SPIE.7740E..66K}.

@@

The \model{COM} model is the common-mode signal itself
($\mathbf{n}^{c}(t)$ in Eq.~\ref{eq:noise}). It is a single time
series that is estimated by finding the mean of all bolometers at each
time step. Bolometer values that have been flagged as unusable are
excluded from the mean.

Even after flat-fielding, bolometers may have slightly varying
sensitivities and so the amplitude of the common-mode variations will
also vary from bolometer to bolometer. Comparing each bolometer
time-series with the common-mode signal allows an estimate of the
relative bolometer sensitivity to be obtained. In practice, a least
squares linear fit is performed between the bolometer time-series and
the common-mode to determine a gain ($g_i$ in Eq.~\ref{eq:noise}) and
offset for each bolometer.  The gain and offset for each bolometer is
known as the \model{GAI} model. Each bolometer value can then
optionally be scaled and shifted using these values so that all
bolometers share a common (but as yet unknown) calibration. This
provides an alternative (or additional) flat-fielding strategy to that
described in Section~\ref{sec:bolos}.

@@

The primary purpose of the noise component, \model{NOI}, is to measure
the white noise levels of each bolometer ($\mathbf{n}^\mathrm{w}_i(t)$
in Eq.~\ref{eq:noise}). The measurement generally occurs once all of
the other models have been fit and removed. This noise may then be
used to estimate weights for the data in subsequent iterations.

@@

%------------------------------------------------------------------------------
\section{Summary and future work}
\label{sec:summary}
%------------------------------------------------------------------------------

>>>>

In order to reduce the impact of low-frequency noise on the final
maps, \scuba\ scan strategies have been designed to provide: (i) good
cross-linking (visiting every point of the mapped area on several
different time scales, and at different scan angles); and (ii) minimal
accelerations to reduce turn-around overheads (which could be quite
large given the 600\,arcsec\,s$^{-1}$ maximum scan speed). For areas
larger than the array footprint a rectangular ``PONG'' pattern is
used, in which the boresight travels in approximately straight lines
and ``bounces'' off the edges at 45\,degree angles until the area is
uniformly filled in. It is also usually combined with a rotation
through a number of fixed position angles to create a ``rotating
PONG'' with even better cross-linking. For smaller areas (of order the
array footprint, or pont sources), in which the PONG turn-around
overheads would be large, a ``constant velocity daisy'' (CV Daisy) is
used.  Here the telescope moves in a circle, whose centre also slowly
traces out a small circle. For a more complete description of the
\scuba\ observing modes, see Section~5 in \citet{holland2012} and also
\citet{2010SPIE.7740E..66K}.

@@

The \model{COM} model is the common-mode signal itself
[$\mathbf{n}^{c}(t)$ in Eq.~\ref{eq:noise}]. It is a single time
series that is estimated by finding the mean of all bolometers at each
time step. Bolometer values that have been flagged as unusable are
excluded from the mean.

Even after flat-fielding, bolometers may have slightly varying
sensitivities and so the amplitude of the common-mode variations will
also vary from bolometer to bolometer. Comparing each bolometer
time-series with the common-mode signal allows an estimate of the
relative bolometer sensitivity to be obtained. In practice, a least
squares linear fit is performed between the bolometer time-series and
the common-mode to determine a gain [$g_i$ in Eq.~\ref{eq:noise}] and
offset for each bolometer.  The gain and offset for each bolometer is
known as the \model{GAI} model. Each bolometer value can then
optionally be scaled and shifted using these values so that all
bolometers share a common (but as yet unknown) calibration. This
provides an alternative (or additional) flat-fielding strategy to that
described in Section~\ref{sec:bolos}.

@@

The primary purpose of the noise component, \model{NOI}, is to measure
the white noise levels of each bolometer [$\mathbf{n}^\mathrm{w}_i(t)$
in Eq.~\ref{eq:noise}]. The measurement generally occurs once all of
the other models have been fit and removed. This noise may then be
used to estimate weights for the data in subsequent iterations.

@@

%------------------------------------------------------------------------------
\section{Conclusions}
\label{sec:conclusions}
%------------------------------------------------------------------------------
